---
title: 20INMCAL204- Laboratory Report
author:
  - name: Jayaraj J Pillai
    email: jayaraj.inmca2025@saintgits.org
    affiliation: Student, INMCA 20-25
    correspondingauthor: true
    footnote: 1
  - name: Siju K.S
    email: siju.swamy@saintgits.org
    affiliation: Saintgits College of Engineering (Autonomous)
    footnote: 2
  - name: Jobin Jose
    email: jobin.jose@saintgits.org
    affiliation: Saintgits College of Engineering (Autonomous)
    footnote: 2
address:
  - code: Student, INMCA 20-25
    address: Department of Computer Applications, RB402
  - code: Saintgits College of Engineering (Autonomous)
    address: Department of Mathematics, AB304
footnote:
  - code: 1
    text: "Student, 20INMCAL204."
  - code: 2
    text: "Course Faculty, 20INMCAL204."
abstract: |
 Experiments listed in the Lab Manual are successfully executed in the R version 4.1.0. Details of the experiments with input \& ouput are summerized in the form of a report. Experiments are arranged in the form of sections. This report is prepared using the R-package `rticles` [@mrticles].
journal: "Mathematics Department for Evaluation"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: true
numbersections: true
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
editor_options: 
  markdown: 
    wrap: 72
---

```{=tex}
\tableofcontents
\newpage
```
## Question-1

Calculate the coefficient of correlation for the ages of husbands and wives.

$\begin{array}{|l|cccccccc|}\hline \text{Age of Husband (Years)}& 23& 27& 28& 29& 30& 31& 33& 35& 36& 39\\\hline \text{Age of Wife (Years)   }& 18& 22& 23& 24& 25& 26& 28& 29& 30& 32\\\hline \end{array}$

## R code

```{r}
# loading data
H=c(23, 27, 28, 29, 30, 31, 33, 35, 36, 39)
W=c(18, 22, 23, 24, 25, 26, 28, 29, 30, 32)
```

### Calculating correlation coefficient

```{r}
resp2=cor.test(H,W,method='pearson')
```

### Displaying the correlation

```{r}
resp2
```

## Results and discussion

Since the correlation coefficient of the given variables = 0.99, the value is highly positively correlated.

## Question-2

The ranks of the same 15 students in two subjects Statistics and Accountancy are given below, the two numbers within the brackets denoting the ranks of the same students in Statistics and Accountancy respectively. (1,10), (2,7), (3,2), (4,6), (5,4), (6,8), (7,3), (8,1), (9,11), (10,15), (11,9), (12,5), (13,14), (14,12), (15,13). Use Spearman's formula to find the rank correlation coefficient.

## R code

```{r}
# loading data
S=c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15)
A=c(10, 7, 2, 6, 4, 8, 3, 1, 11, 15, 9, 5, 14, 12, 13)
```

### Calculating correlation coefficient

```{r}
ress3=cor.test(S,A,method='pearson')
```

### Displaying the correlation

```{r}
ress3
```

## Results and discussion

Since the correlation coefficient of the given variables = 0.51, the value is positively correlated.

## Question-3

From the following data, obtain the two regression equations:

$\begin{array}{lllllllllll} Sales: & 91 & 97 & 108 & 121 & 67 & 124 & 51 & 73 & 111 & 57 \\ Purchases: & 71 & 75 & 69 & 97 & 70 & 91 & 39 & 61 & 80 & 47 \end{array}$

## R code

```{r}
# create input parameters
marketing=data.frame(sales=c(91,97,108,121,67,124,51,73,111,57),Purchases=c(71,75,69,97,70,91,39,61,80,47))
```

### Checking Association

```{r}
cor.test(marketing$sales,marketing$Purchases,method="pearson")
```

### Create the OLS model

```{r}
#fit a linear model
model <- lm(sales ~ Purchases, data = marketing)
```

```{r}
summary(model)$coef
```

```{r}
model <- lm(Purchases ~ sales, data = marketing)
summary(model)$coef
```

## Results and Discussions

### case 1

The regression equation result is: $-5.188285 , 1.359833$

### case 2

The regression equation result for is : $14.8113208 , 0.6132075$

## Question-4

The production manager of a company maintains that the flow time in days (y), depends on the number of operations (x) to be performed. The following data give the necessary information:

$\begin{array}{|l|l|l|l|l|l|l|l|l|l|l|}\hline x & 2 & 2 & 3 & 4 & 4 & 5 & 6 & 6 & 7 & 7 \\ \hline y & 8 & 13 & 14 & 11 & 20 & 10 & 22 & 26 & 22 & 25 \\ \hline \end{array}$

Calculate the value of the Karl Pearson's Correlation Coefficient.

## R code

```{r}
# loading data
x=c(2, 2,	3, 4,	4, 5,	6, 6,	7, 7)
y=c(8, 13, 14, 11, 20, 10, 22, 26, 22, 25)
```

### Calculating correlation coefficient

```{r}
ress4=cor.test(x,y,method='pearson')
ress4
```

## Results and Discussions

Since the correlation coefficient of the given variables = 0.781513 , the value is highly positively correlated.

## Question-5

Calculate Spearman's rank correlation coefficient between advertisement cost and sales from the following data.

$\begin{array}{|l|l|l|l|l|l|l|l|l|l|l|} \hline Advertisement cost (‘000 Rs) & 39 & 65 & 62 & 90 & 82 & 75 & 25 & 98 & 36 & 78 \\ \hline Sales (LakhsRs.) & 47 & 53 & 58 & 86 & 62 & 68 & 60 & 91 & 51 & 84 \\ \hline \end{array}$

## R code

```{r}
# loading data
A=c(39, 65, 62, 90, 82, 75, 25, 98, 36, 78)
S=c(47, 53, 58, 86, 62, 68, 60, 91, 51, 84)
```

### Calculating correlation coefficient

```{r}
ress5=cor.test(S,A,method='spearman')
ress5
```

## Results and Discussions

Since the correlation coefficient of the given variables = 0.818, the value is highly positively correlated.

## Question-6

From the data given below, find the two regression equations

\begin{array}{|l|l|l|l|l|l|l|l|l|l|l|}
\hline
\begin{array}[c]{@{}l@{}}Marks in \\ Economics\end{tabular}  & 25 & 28 & 35 & 32 & 31 & 36 & 29 & 38 & 34 & 32 \\ \hline
\begin{array}[c]{@{}l@{}}Marks in \\ Statistics\end{tabular} & 43 & 46 & 49 & 41 & 36 & 32 & 31 & 30 & 33 & 39 \\ \hline
\end{array}

##R-code

```{r}
marketing=data.frame(Economics=c(25,28,35,32,31,36,29,38,34,32),Statistics=c(43,46,49,41,36,32,31,30,33,39))
```

```{r}
cor.test(marketing$Economics,marketing$Statistics,method="pearson")
```

### Create the OLS model

```{r}
#fit a linear model
model <- lm(Economics ~ Statistics, data = marketing)
```

```{r}
summary(model)$coef
```

```{r}
model <- lm(Statistics ~ Economics, data = marketing)
summary(model)$coef
```
## Results and Discussions

### case 1

The regression equation result is: $40.8793970 , -0.2336683$

### case 2

The regression equation result for is : $59.2571429 , -0.6642857$


##  Question-7

A die was thrown 9000 times and of these 3220 yielded a 3 or 4.Can the die be regarded as unbiased?

## R-code

```{r}
prop.test(x=3220,n=9000,p=1/3,alternative = 'two.sided')
```

## Result and discussion

Here the p value is 9.193e-07 which is greater than 5% significant level. Null hypothesis is rejected. So it is statistically reasonable to conclude that the die which was thrown 9000 times and of these 3220 yielded a 3 or 4 cannot be regarded as unbiased.

## Question-8

In a random sample of 400 persons from a large population, 120 are females. Can it be said that males and females are in the ratio 5:3 in the population? Use 1% significance?

## R-code

```{r}
prop.test(x=120,n=400,p=3/8,alternative = 'two.sided')
```

## Results and Discussions

Since the p-value is less than 0.05, the null hypothesis is rejected at 5 percent significance level. So it is reasonable to conclude that the ratio of male to female is 5:3.

## Question-9

The adjoining table shows the number of motor registrations in a certain territory for a 230 term of 5 years and the sale of motor tyre by a firm in that territory for the same period.

+----------------+----------------+------------------------+
| Year           | Motor          | No of Sales            |
|                | Registration   |                        |
| 1              |                | 1250                   |
|                | 600            |                        |
+----------------+----------------+------------------------+
| 2              | 630            | 1100                   |
+----------------+----------------+------------------------+
| 3              | 720            | 1300                   |
+----------------+----------------+------------------------+
| 4              | 750            | 1350                   |
+----------------+----------------+------------------------+
| 5              | 800            | 1500                   |
+----------------+----------------+------------------------+

Find the regression equation to estimate the sale of Tyres when motor registration is known. Estimate 233 sale of Tyre when registration is 850.

## R-code

```{r}
marketing=data.frame(X=c(600,630,720,750,800),Y=c(1250,1100,1300,1350,1500))
cor.test(marketing$X,marketing$Y)
```
```{r}
model <- lm(Y ~ X , data = marketing)
summary(model)$coef

```

## Results and Discussions

From the given data, an OLS model is created using R function lm(). In our example, the fitted linear model is:
Sale of Tyre = 255.035971 + 1.492806(Motor registration), it can be seen that p-value of the F-statistic is 0.06567.

## Question-10

In a big city 325 men out of 600 men were found to be smokers. Does this information support the conclusion that the majority of men in this city are smokers? Justify your answer statistically.

## R-code

```{r}
prop.test(x=325,n=600,p=1/2,alternative = 'greater')

```

## Results and Discussions

Since the p-value is less than 0.05, the null hypothesis is rejected at 5 percent significance level. So it is reasonable to conclude that the ratio of smokers to non smokers is greater than 50%.

## Question-11

The mean height of 500 male students who showed above average participation in college athletics was 75.2 inches with a standard deviation of 2.3 inches; while 500 male students who showed no interest in such participation had mean height of 68.5 inches with a standard deviation 2.9 inches. Test the hypothesis that male students who participate in college athletics are taller than other male students.

## R-code

```{r}
library(BSDA)
```
```{r}
zsum.test(mean.x = 75.2,n.x = 500,sigma.x = 75.2,
mean.y = 68.5,n.y = 500,sigma.y = 2.9,alternative = 'greater')
```
## Results and Discussions

Since the p-value is less than 0.05, the null hypothesis is rejected at 5 percent significance level. So it is reasonable to conclude that the mean height of male students shows above average participation are significantly taller.
