---
title: "Experiment-16 :Perform the Z test for single proportion"
author: "prudhwi.inmca2025@saintgits.org"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

To perform the Z- test for single proportion

## Algorithm

-   Step 1: Assign the inputs and formulated the hypothesis

-   Step 2: Write the proportion test commands in code chunk

-   Step 3: Report the results

-   Step 4: Interpret the result and write calculation

## Hypothesis

The hypothesis based on information given in case are:

H~0~ : p=0.5 H~1~ : p\>0.5

## R code

```{r}

maleX=95
pnot<-0.5
samplesize=160

```

```{r}

resprop=prop.test(x = maleX,n = samplesize,p = pnot,correct = FALSE,conf.level =0.95,alternative ="greater")

```

```{r}
resprop

```

## Result & discussions 

Here the p value is 0.008853-which is >0.5.Null hypothesis is rejected at 5% level.
So it is statistically reasonable to include that cancer effects more males than females.
