---
title: "Experiment 4"
author: "jayu1294@gmail.com"
date: '2022-04-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

1. To create the statistical summary of a data

2. To study normality of the data

## Packages used and syntax of R methods

For statistical summary of a given dataset, the `rbase` package will be used. To calculate skewness and kurtosis of dataset, the `ACSWR` is used.

>*Note:* The functions `skewness` and `kurtosis` from the `e1071` package are more generic functions. Another resouse is `moments` package. 

## Algorithm
* Step 1: Load the dataset

* Step 2: Load necessary packages

* Step 3: Calculate statistical summaries

* Step 4: Calculate the `skewness` and `kurtosis` of the numerical data

* Step 5: Report the results

## R code

```{r}
#loading package
library(ACSWR)
#loading data
data(yb)
#view structure of data
str(yb)

```
```{r}
# creating statistical summary

summary(yb)
```
```{r}
range(yb$Preparation_1); range(yb$Preparation_2) # list out ranges of data

```

```{r}
#skewness and kurtosis of preparation_1
skewcoeff(yb$Preparation_1); kurtcoeff(yb$Preparation_1)
```
```{r}
#skewness and kurtosis of preparation_2
skewcoeff(yb$Preparation_2); kurtcoeff(yb$Preparation_2)
```
## problems
1. a=1,4.8,12 and b=4,8,12,16 find(1). summary(2).
skewness and kurtosis

**SOLUTION**
```{r}
a=c(1,4,8,12)
b=c(4,8,12,16)
```
```{r}
summary(a)
```
```{r}
summary(b)
```
```{r}
skewcoeff(a);kurtcoeff(a)
```
```{r}
skewcoeff(b);kurtcoeff(b)
```


## Results & discussions

A distribution is normal then `mean=median=mode` and the skewness is 0 and kurtosis is 2. In this experiment statistical summaries of two variables are created. From the skewness and kurtosis measures, both the variables are positively skewed and `preparation_1` is lepto-kurtic and `preparation_2` is meso-kurtic. Based on the statistical summary and skewness and kurtosis measures, both the variables are different from a normal distribution.