---
title: 'EXPERIMENT 15: Compute confidence intervals for the mean when the standard
  deviation is known.'
author: "jayaraj.inmca2025@saintgits.org"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AIM
1. To compute confidence intervals for the mean of a given dataset.

## PACKAGES USED AND SYNTAX OF R METHODS

Functions from stats packages (which is loaded by default) is used.

## ALGORITHM

**STEP 1:** Assign the inputs.

**STEP 2:** Find the mean, variance and S.E.

**STEP 3:** Calculate a 95% confidence interval for mean using the formula $\bar{X}\pm1.96*S.E$.

**STEP 4:** Return the confidence intervals(LCL and UCL).

case: Calculate a 95% confidence interval for mean if $S.E=\frac{SD}{\sqrt{n}}$.

## R CODE

# Create input parameters
```{r}
xbar<-12
stddev<-3
n<-30
```

# Calculating 95% confidence interval for the mean

```{r}
S.E=stddev/sqrt(n)
error<-qnorm(0.975)*S.E
lower_bound<-xbar - error
upper_bound<- xbar + error
```

# Displaying the LCL and UCL
```{r}
lower_bound
```
```{r}
upper_bound
```

## RESULTS AND DISCUSSIONS

The 95% confidence interval for mean is calculated as (10.9264835, 13.0735165).
