---
title: "Experiment 12: Correlation analysis- Spearman Rank Correlation Coefficient"
author: "siju.swamy@saintgits.org"
date: "4/23/2022"
output:  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

1. To find the Spearman rank correlation coefficient of the given bivariate data

## Packages used and syntax of R methods

Functions from `stat` package (which is loaded by default). 

**Pearson correlation (r)**, which measures a linear dependence between two variables (x and y). It’s also known as a parametric correlation test because it depends to the distribution of the data. It can be used only when x and y are from normal distribution. The plot of $y = f(x)$ is named the linear regression curve. The Spearman correlation method computes the correlation between the rank of x and the rank of y variables.

$$ rho = \frac{\sum(x' - m_{x'})(y'_i - m_{y'})}{\sqrt{\sum(x' - m_{x'})^2 \sum(y' - m_{y'})^2}}$$


where $x'=rank(x)$ and $y'=rank(y)$.

Correlation coefficient can be computed using the functions `cor()` or `cor.test()`:

**Syntax:**

> `cor(x, y, method = c("pearson", "kendall", "spearman"))`
 `cor.test(x, y, method=c("pearson", "kendall", "spearman"))`

>Note: If the data contain missing values, use the following R code to handle missing values by case-wise deletion.

`cor(x, y,  method = "pearson", use = "complete.obs")`

## Algorithm

* Step 1: Assign the inputs for required correlation model

* Step 2: Calculate the correlation coefficient

* Step 3: Interpret the result



>*Case:*  The scores for nine students in history and algebra are as follows:

$\begin{array}{|l|cccccccc|}\hline
\text{History}:&35& 23& 47& 17& 10& 43& 9& 6&28\\\hline
\text{Algebra}:&30& 33&45&23&8&49&12&4&31\\\hline
\end{array}$

Compute the Spearman rank correlation.


## R code

```{r}
# loading data
History=c(35,23,47,17,10,43,9,6,28)
Algebra=c(30,33,45,23,8,49,12,4,31)
```



### Calculating correlation coefficient

```{r}
ress3=cor.test(History,Algebra,method='pearson')
ress3
```


### Plotting the variables
```{r}
my_data=data.frame(History=History,Algebra=Algebra)
head(my_data)
```



```{r Scattercor, fig.cap='Scatter plot with smooth fit curve', out.width='80%', fig.asp=.75, fig.align='center',warning=FALSE}

library(ggpubr)
ggscatter(my_data, x = "History", y = "Algebra", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "Marks in History", ylab = "Marks in Algebra")
```



## Results & discussions

Correlation coefficient of given bivariate data is calculated using built-in function in `stats` package. 

The Spearman rank correlation coefficient is `r ress3$estimate`. Also p-value is `r ress3$p.value ` >0.05. So the null hypothesis is rejected. So it is statistically reasonable to conclude that there is  significant positive correlation between the marks of the samples.