---
title: "Experiment 10: Correlation analysis- Karl-Pearson Coefficient of Correlation"
author: "siju.swamy@saintgits.org"
date: "4/23/2022"
output:  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

1. To find the correlation coefficient of the given bivariate data

## Packages used and syntax of R methods

Functions from `stat` package (which is loaded by default). 

**Pearson correlation (r)**, which measures a linear dependence between two variables (x and y). It’s also known as a parametric correlation test because it depends to the distribution of the data. It can be used only when x and y are from normal distribution. The plot of $y = f(x)$ is named the linear regression curve. The Pearson correlation formula is:
$$r = \frac{\sum{(x-m_x)(y-m_y)}}{\sqrt{\sum{(x-m_x)^2}\sum{(y-m_y)^2}}}$$ 

where $m_x$ and $m_y$ are means of the distributions x and y respectively.

Correlation coefficient can be computed using the functions `cor()` or `cor.test()`:

**Syntax:**

> `cor(x, y, method = c("pearson", "kendall", "spearman"))`
 `cor.test(x, y, method=c("pearson", "kendall", "spearman"))`

>Note: If the data contain missing values, use the following R code to handle missing values by case-wise deletion.

`cor(x, y,  method = "pearson", use = "complete.obs")`

## Algorithm

* Step 1: Assign the inputs for required correlation model

* Step 2: Calculate the correlation coefficient

* Step 3: Verify the result using direct calculation

* Step 4: Interpret the result


>*Case:*  From the following data, compute Karl Pearson's coefficient of correlation.

$\begin{array}{|l|ccccccc|}\hline
\text{Price(Rupees)}:& 10& 20& 30& 40& 50& 60& 70\\\hline
\text{Supply(Units)}:& 8& 6& 14& 16& 10& 20& 24\\\hline
\end{array}$


## R code

```{r}
# loading data
price=c(10,20,30,40,50,60,70)
supply=c(8,6,14,16,10,20,24)
```



### Calculating correlation coefficient

```{r}
resp1=cor.test(price,supply,method='pearson')
resp1
```

### Direct calculation

Formula is: $$r = \frac{\sum{(x-m_x)(y-m_y)}}{\sqrt{\sum{(x-m_x)^2}\sum{(y-m_y)^2}}}$$ 

```{r}
#direct calculation
rho=(sum(((price-mean(price))*(supply-mean(supply)))))/(sqrt(sum((price-mean(price))^2)*(sum((supply-mean(supply))^2))))
rho
```

### Plotting the variables
```{r}
my_data=data.frame(price=price,supply=supply)
head(my_data)
```



```{r Scattercor, fig.cap='Scatter plot with smooth fit curve', out.width='80%', fig.asp=.75, fig.align='center',warning=FALSE}

library(ggpubr)
ggscatter(my_data, x = "price", y = "supply", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Price", ylab = "Supply")
```



## Results & discussions

Correlation coefficient of given bivariate data is calculated using built-in function in `stats` package. The result is verified using direct calculation.

Since the Pearson coefficient is `r resp1$estimate`. Also p-value is `r resp1$p.value ` <0.05. So the null hypothesis is accepted. So it is statistically reasonable to conclude that there is a significant positive correlation between the price and supply based on the sample.