---
title: "EXPERIMENT 5"
author: "jayu1294@gmail.com"
date: '2022-04-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

1. To calculate Bayes posterior probability using Bayes theorem

## Packages used and syntax of R methods

Bayes posterior probability can be directly calculated using mathematical method or using the package `LaplacesDemon`.

## Algorithm
* Step 1: Load the package, prior probabilities and conditionals

* Step 2: Calculate the Bayes posterior probability using the formula-$P(B_j|A)=\dfrac{P(A|B_j)P(B_j)}{\sum\limits_{j=1}^mP(A|B_j)P(B_j)}$

* Step 3: Calculate the same prior probability using `LaplaceDemon` package

* Step 4: Report the results

>*Case:* Classical Problem from Hoel, Port, and Stone (1971). Suppose there are three tables with two drawers each. The first table has a gold coin in each of the drawers, the second table has a gold coin in one drawer and a silver coin in the other drawer, while the third table has silver coins in both of the drawers. A table is selected at random and a drawer is opened which shows a gold coin. 

>*Observation:*The problem is to compute the probability of the other drawer also showing a gold coin. The Bayes formula can be easily implemented in an R program.

## R code

```{r}
#loading data
prob_GC <- c(1,1/2,0)
priorprob_GC <- c(1/3,1/3,1/3)
```

```{r}
#calculating postrior probability
post_GC <- prob_GC*priorprob_GC
post_GC/sum(post_GC)
```

```{r}
# do the same using LaplacesDemon` package
library(LaplacesDemon)
BayesTheorem(prob_GC, priorprob_GC)

```


## Results & discussions

The Bayes theorem is used to calculate posterior probability of the Mathematical model of the given case. Also the reslut is verified using the `LaplacesDemon` package.