---
title: "EXPERIMENT 6"
author: "jayu1294@gmail.com"
date: '2022-04-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

1. To calculate probability mass density, probability distribution and quantiles using binomial distribution

## Packages used and syntax of R methods

Functions from `stat` package (which is loaded by default). 

The probability mass at a point $x$ can be evaluated using the syntax:

>`dbinom(x=x,size=n,p=p)`.

The probability distribution $P(X\leq x)$ is calculated using the `pbinom()` function. Syntax is: 

>`pbinom(x,size=n,p=p)`

The quantile for probability $p$ can be evaluated using the `quantile()` function. Syntax is:

>`qbinom(prob,size,p=p)`

## Algorithm

* Step 1: Assign the inputs for required distribution

* Step 2: Calculate the required probabilities

* Step 3: Report the results


>*Case:* Find the mass function of a binomial distribution with  $n=20,p=0.4$. Also draw the graphs of the mass function and cumulative distribution function.

## R code

```{r}
# create input parameters
n=20
p=0.4
x=0:20
```
### Prbability distribution

```{r}
#calculating probability mass distribution and cumulative distribution
pmval=dbinom(x,size=n,prob=p)
pmval
```

## Cumulative probability distribution

```{r}
#calculating cumulative density
cdval=pbinom(x,size=n,prob=p)
cdval
```
### Plotting the `pmf` and `cdf`

```{r}
par(mfrow=c(1,2))
plot(x,pmval,xlab="x",ylab="P(X=x)", main="The Binomial Distribution")
plot(x,cdval,xlab="x",ylab=expression(P(X<=x)),main="Cumulative Distribution Function")

```


## Results & discussions

The `pmf` and `cf` of the Binomial distribution for given input parameters are evaluated and create respective plots.