---
title: 'Experiment 7: Poisson Distribution'
author: "jayu1294@gmail.com"
date: "4/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

1. To calculate probability mass density, probability distribution and quantiles using Poisson distribution

## Packages used and syntax of R methods

Functions from `stat` package (which is loaded by default). 

The probability mass at a point $x$ can be evaluated using the syntax:

>`dpois(x=x,lambda=l)`.

The probability distribution $P(X\leq x)$ is calculated using the `ppois()` function. Syntax is: 

>`pbinom(x,lambda=l)`

The quantile for probability $p$ can be evaluated using the `qpois()` function. Syntax is:

>`qpois(prob,lambda=l)`

## Algorithm

* Step 1: Assign the inputs for required distribution

* Step 2: Calculate the required probabilities

* Step 3: Report the results


>*Case:* Given the data $n=50$, mean, $\lambda=25$, use appropriate function to find the mass function of a Poisson distribution. Also draw the graphs of the mass function and cumulative distribution function.

## R code

```{r}
# create input parameters
n <-50; l <- 25
x=0:50
```
### Prbability distribution

```{r}
#calculating probability mass distribution and cumulative distribution
pmval=dpois(x,lambda=l)
pmval
```

### Cumulative probability distribution

```{r}
#calculating cumulative density
cdval=ppois(x,lambda = l)
cdval
```
### Plotting the `pmf` and `cdf`

```{r}
par(mfrow=c(1,2))
plot(x,pmval,xlab="x",ylab="P(X=x)", main="The Poisson Distribution")
plot(x,cdval,xlab="x",ylab=expression(P(X<=x)),main="Cumulative Distribution Function")

```


## Results & discussions

The `pmf` and `cf` of the Poisson distribution for given input parameters are evaluated and create respective plots.