---
title: 'EXPERIMENT 20: ONE SAMPLE t-test.'
author: "jayaraj.inmca2025@saintgits.org"
date: '2022-06-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AIM

1.  To implement one sample t-test in R.

## PACKAGES USED AND SYNTAX OF R METHODS

To perform one-sample t-test, the R function t.test() can be used as follow:

> Syntax: 't.test(x, mu=0,alternative=c("greater,""less,""two.sided")'

## ALGORITHM

**Step 1:** Assign the inputs.

**Step 2:** Apply t-test.

**Step 3:** Interpret the result.

*case:* Weight of 10 mice to test whether the average weight of the mice population is 25g or not.

\begin{array}{|l|l|l|l|l|l|l|l|l|l|l|}
\hline
Sample no:  & 1    & 2    & 3    & 4    & 5    & 6    & 7    & 8    & 9    & 10  \\ \hline
Weight (g): & 17.6 & 20.6 & 22.2 & 15.3 & 20.9 & 21.0 & 18.9 & 18.9 & 18.9 & 18.2 \\ \hline
\end{array}

## R CODE

```{r}
#loading data
w=c(17.6,20.6,22.2,15.3,20.9,21.0,18.9,18.9,18.9,18.2)

```

## APPLY ONE SAMPLE t test

```{r}
# One-sample t-test
rest1<- t.test(w, mu = 25)
# Printing the results
rest1
```

## RESULTS AND DISCUSSIONS

The p-value of the test is 0.0005073 , which is less than the significance level alpha = 0.05. We can conclude that the mean weight of the mice is significantly different from 25g with a p-value = 0.0005073
