---
title: "EXPERIMENT-17: Perform the Z-test for two proportions"
author: "prudhwi.inmca2025@saintgits.org"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## [Aim:]{.underline}

To perform the Z-test for two proportions

## [Packages used and syntax of R methods:]{.underline}

Functions from `stats` package are used.Syntax is:

> **`prop.test(x=c(A,B),n=c(n1,n2),p=NULL,alternative=c("two.sided","greater","less",correct=TRUE))`**

## [Algorithm:]{.underline}

-   Step 1: Assign the inputs and formulate the hypothesis

-   Step 2: Write the two-proportions test commands in code chunk

-   Step 3: Report the result.

-   Step 4: Interpret the results and write the conclusion

***Case:** Two groups with sample size 500 are selected to study the impact of smoking habit on the incidents of lung-cancer. Group A with lung cancer contains 490 smokers. While Group B of healthy individuals contains 400 smokers. Examine whether smoking causes cancer based on this data*

## [Hypothesis:]{.underline}

The Hypothesis based on information given in the case are:

*H~0~* : *p~1~* = *p~2~ H~1~* : *p~1~* ≠ *p~2~* (right tailed test)

## [R code:]{.underline}

```{r}
# create input parameters
n1=500;n2=500
cancersmoke=490
healthysmoke=400
```

#### **Calculating 95% confidence interval for the mean**

```{r}
#apply single proportion test on the large sample
resprop2=prop.test(x=c(cancersmoke,healthysmoke),n=c(n1,n2),conf.level = 0.95,alternative = "two.sided")
```

#### **The test result**

```{r}
# call the test results
resprop2
```

## [Results & Discussions:]{.underline}

The p-value of the test is $2.2e-16$,which is less than the signature level alpha=$0.05$. We can conclude that the proportion of smokers is significantly different in the two groups with a p-value=$2.2e-16$.More over the proportion of smokers in cancer patients is high($98%$).So it is reasonable to conclude that smoking causes cancer
