---
title: 'EXPERIMENT 14: CPNTRUCT A SCATTERPLOT TO INVESTIGATE BETWEEN TWO VARIABLES'
author: "jayaraj.inmca2025@saintgits.org"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AIM

1. To investigate between two given variables.

## PACKAGES USED AND SYNTAX OF R METHODS

Functions from stats package (which is loaded by default). For plotting the scatter points,the geom_point() function from ggplot2 package and cor.test() function from stats packages are used.

## ALGORITHM

**STEP 1:** Assign the inputs for required comparison.

**STEP 2:** Create scatter plot using plot() function in R.

**STEP 3:** Report the observations.

**STEP 4:** Confirm the observations using correlation analysis.

case: Identify the relationship between sales units based on advertising budget spent on youtube. The sales data with corresponding expenditure in youtube is shown below:
 
\begin{array}{|l|l|l|l|l|l|l|l|}
\hline
SALES(Y):             & 2 & 4 & 6 & 9 & 12 & 34 & 45 \\ \hline
ADD EXPENSE(YOUTUBE): & 1 & 2 & 4 & 7 & 9  & 11 & 15 \\ \hline
\end{array}

## R CODE

#create input parameters
```{r}
marketing= data.frame(sales=c(2,4,6,9,12,34,45),youtube=c(1,2,4,7,9,11,15)) 
```
##plotting the data as d scatter diagram

```{r}
library(ggplot2)
ggplot(marketing,aes( x = youtube, y = sales))+
  geom_point()+
  stat_smooth()
```

## checking association
```{r}
cor.test(marketing$sales,marketing$youtube)
```
##RESULTS AND DISCUSSIONS

The given variables are plotted using ggplot2 package. From the plot it is clear that there is a linear relationship between the variables. The correlation coefficient is 0.9267856. So the linear association is highly significant at 5% significance level.  
